---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ArgosQC

<!-- badges: start -->
<!-- badges: end -->

An R package to conduct unsupervised location quality-control of IMOS-deployed SMRU SRDL-CTD tag data in near real-time. {ArgosQC} automatically does the following:

1. accesses SMRU or WC tag data from a local file source or from manufacturer's Data portal
2. organizes the multi-file data structures
3. organizes associated deployment metadata
4. collates the tag data with deployment metadata
5. fits SSM's to species-specific subsets of the data
6. appends SSM-estimated locations to every tag-measured event record (CTD, dive, haulout, raw Argos location, raw GPS location, etc)
7. writes appended tag files to .csv in a user-specified output directory

The SMRU SRDL-CTD tag QC process is detailed in the IMOS [Best Practice Manual](https://repository.oceanbestpractices.org/handle/11329/2571). The Wildlife Computers tag QC process follows an analogous workflow that accommodates the manufacturer's tag data file structures.

## Installation

You can install the main version of ArgosQC from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ianjonsen/ArgosQC")
```

## Example

ArgosQC workflows can be run via single functions, specific to the AniBOS Program (ATN, IMOS, etc...) and the tag manufacturer - currently, SMRU (`smru`) or Wildlife Computers (`wc`):

```{r example, eval = FALSE}
library(ArgosQC)

smru_qc(wd = "test", config = "test_conf.json")
```



# Acknowledgements:

### Financial support for the development of this software is provided by:

#### [LOCEAN, France](https://www.locean.ipsl.fr) via Laurent MORTIER & Jean-Benoît CHARRASSIN

#### [Armines, France](https://www.armines.net/fr) via Laurent MORTIER

#### [IMOS, Australia](https://imos.org.au) & [SIMS, Australia](https://sims.org.au) via Robert HARCOURT & Clive MCMAHON
