---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ArgosQC)
```

## Background
`ArgosQC` provides automated workflows for quality controlling Argos & GPS (when present) locations obtained from either SMRU SRDL or Wildlife Computers animal telemetry tags. Workflows currently are set up for IMOS and ATN tagging data. The general workflow for SMRU tags is documented in [Jonsen et al. 2024](https://repository.oceanbestpractices.org/handle/11329/2571). The workflow for Wildlife Computers tags is analogous but not identical due to differences in both the structure and nature of the data the tags collect and transmit.

## Workflows
Several automated QC workflows have been set up for SMRU SRDL-CTD (and related) tags, and for Wildlife Computers SPOT, SPLASH and SCOUT tags. The workflows are specific to IMOS - AODN and ATN metadata and QC output data structure requirements. The following QC workflows can be implement from a single `ArgosQC` function & a required config JSON file, with output written to .CSV files in a user-specified directory:

|             Workflow                                   |    Function         |
|:------------------------------------------------------:|:-------------------:|
| SMRU SRDL-CTD (and related) tags +  IMOS metadata      |  `smru_qc()`   |
| SMRU SRDL-CTD (and related) tags + ATN metadata        |  `smru_qc()`    |
| Wildlife Computers SPOT, SPLASH, and SCOUT tags + ATN metadata   |  `wc_qc()`      |
| Wildlife Computers tag data + Generic metadata         |  `wc_qc()`      |


These single function workflows simplify the automated QC implementation. Additional workflows will be added as required to accommodate additional tag manufacturers and/or tag data structures, as well as organisational metadata and output data formatting requirements. The QC workflows can also be implemented by calling individual `ArgosQC` functions in series as required. This latter approach allows greater flexibility as intermediate & final output data and metadata can be re-structured as needed. The single function SMRU & Wildlife Computers tag workflows are outlined in `vignette('SMRU SRDL-CTD tag QC workflow')`




